Shaping Anti-Corruption Campaigns in Nigeria

### 2024-12-04 paper/paper.qmd
data_diary

---
title: "Shaping Anti-Corruption Campaigns in Nigeria"
subtitle: "Youth Populations, Urban Areas and Moderately Educated Citizens Are Important for Anti-Corruption Campaigns "
author: 
  - Fatimah Yunusa
thanks: "Code and data are available at:https://github.com/fatimahsy/Nigeria_Democracy-"
date: today
date-format: long
abstract: "Peceptions of corruption in the Nigerian presidency vary significantly across demogrpahic groups. Using Afrobarometer survey data and Bayesisan ordinal logistic regression, this study looks at how education, gender, age, and urban versus rural residence influence these perceptions. The results show that urban residents and yourger individuals are more likely to perceive high corruption, while rura populations and those with higher education show views that are moderate. These results show the need for targeted anti-corruption campaigns to adress demographic differences and imporve governance accountability in Nigeria"
format: pdf
toc: true
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

Corruption is a very big challenge to governance and development in Nigeria as a result of its ability to undermine public trust and economic growth. As the United Nations Office on Drugs and Crime (UNODC) stated, "corruption affects the lives of ordinary Nigerian, impeding development and eroding public trust in institutions [@corruptionsurvey2024]. This paper looks into the role of demographic factors-education,gender,age, and urban versus rural residence-in shaping perceptions of corruption in the Nigerian presidency.

Primarily, this paper is aimed at understanding how different demographic groups perceive corruption in the Nigerian presidency and to identify ways thiis can help improve anti-corruption campaigns, While existing studies have largely been focused on the institutional dynamics, there seems to be a lack of demographic-specific analysis within the Nigerian context. This paper addresses this gap by making these demographics the focus. It does this by using nationally representative data from Afrobarometer [@afrobarometer2023], a leading survey initiative capturing public attitudes on governance, democracy, and corruption across Africa. A Bayesian ordinal logistic regression was used to find patterns in how education, gender, age, and geographic location influence perceptions of corruption.

Our paper shows that there are alot of disparities in corruption perceptions across demographic groups. Younger respondents and urban residents have higher perceptions of corruption, likely because of higer exposure to investigative media and political discourse. In contrast, rural populations-often reliant on patronage systems- tend to report more neutral views. Education also plays an important role since we find that secondary school graduates have the highest corruption perceptions.

Understanding these demographic differences is important for designing effective anti-corruption campaigns. Making sure outreach efforts are tailored to the unique experiences and perceptions of different demographic groups can increase their effectiveness and increase public trust. For example, youth-focused campaigns that use social media platforms and urban outreach using investigative journalism can engage the people. At the same time, localized, culturally appropriate campaigns in rural areas can address the different needs of these populations. A the UNODC emphasizes, 'targeted and effective anti-corruption policies will improve likes of Nigerian citizens" [@afrobarometer2023].

The remainder of this paper is structured as follows; @sec-data detailed the data used for this paper, @sec-model introduces the Bayesian ordinal logistic regression model used to study the relationship between our variables of interest. @sec-results presents the findings from the model, detailing how different demographic factors like education and age affect corruption perception in Nigeria. @sec-discussion examines these results, discussing their implications for anti-corruption policies, weaknesses and next steps. @sec-survey-appendix explores the details of the Afrobarometer survey. @sec-model-details shows plots for Posterior predictive checks and Diagnostics as well as their analysis. @sec-survey-appendix details the survey methodology used in the Afrobaromenter data and @sec-ethics addresses very important ethical principles and the ethical challenges of surveying sensitive topics like corruption.

@@

For this analysis, i use the Afrobarometer Round 9, Nigeria, 2023
survey. Afrobarometer conducts surveys that are nationally
representative across African nations to capture public perceptions on
topics like governance, democracy, and economic issues. The Nigerian
Round 9 survey dataset contains responses from 1,556 people and shows
the diverse demographic statistics across gender, region, and residence
type(urban or rural). The data is freely available on the Afrobarometer
website[@afrobarometer2023] and was collected through a multi-stage,
stratified sampling method. This is to ensure representativeness and
enables analysis of different demographics and socioeconomic indicators.

@@

The data for this study was downloaded, cleaned, analyzed, modeled, and
visualized using R [@citeR], a statistical programming language.[@afrobarometer2023] served as the primary data source, providing importantsurvey data for analysis.***Telling Stories with Data*** [@tellingstories] was referenced for its code and methodologies. The
following packages were used:

-   **`modelsummary`** [@modelsummary]: Used to create well-formatted
    regression tables and summaries.
-   **`rstanarm`** [@rstanarm]: Facilitated Bayesian regression modeling
    using the Stan backend.
-   **`dplyr`** [@dplyr]: Streamlined data manipulation, transformation,
    and summarization processes.
-   **`here`** [@here]: Simplified the organization of file paths,
    improving project reproducibility.
-   **`arrow`** [@arrow]: Enabled efficient handling of large datasets
    with fast reading and writing capabilities.
-   **`bayesplot`** [@bayesplot]: Assisted in producing diagnostic
    checks and posterior predictive visualizations for Bayesian models.
-   **`ggplot2`** [@ggplot2]: Provided extensive tools for creating
    clear and impactful visualizations.
-   **`patchwork`** [@patchwork]: Combined multiple plots into cohesive,
    professional visuals.
-   **`knitr`** [@knitr]: Enabled dynamic report generation, integrating
    code, output, and text seamlessly.
-   **`kableExtra`** [@kableExtra]: Enhanced table styling and
    formatting for clean, professional presentations.
-   **`ggalt`** [@ggalt]: Allowed the creation of specialized plots,
    enhancing the depth of data visualizations.
-   **`haven`** [@haven]: Facilitated the import of `.sav` survey data
    from the Afrobarometer.
-   **`broom.mixed`** [@broommixed]: Streamlined the extraction and
    tidying of results from mixed models for easy analysis and
    visualization.
-   ***Telling Stories with Data*** [@tellingstories]: This book was
    referenced for its code and methodologies.

@@

# Generate a well-formatted table using kableExtra
kable(
  table_preview, 
  caption = "Preview of the Cleaned Dataset"
) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

@tbl-cleaned-data-preview represents the first six cleaned rows of the
dataset, showing the important variables used in the analysis. The
variables were constructed from specific survey questions in the
Afrobarometer Round 9 Nigeria Survey [@afrobarometer2023], which
captures several socioeconomic sentiments within the country.The column
corruption_presidency captures perceptions of corruption within the
office of the presidency, derived from responses to the question, “How
many of the following people do you think are involved in corruption, or
haven’t you heard enough about them to say: the president and officials
in his office?” The variable education reflects respondents' highest
level of education completed, gathered from the question, “What is the
highest level of education you have completed?” The gender variable
indicates the respondent's gender, collected through direct demographic
inquiry. The column age_group categorizes respondents into age brackets
based on the question, “How old are you?” The urban_rural variable
distinguishes between urban and rural respondents, as recorded by
interviewers based on the primary sampling unit (PSU) during data
collection [@survey_manual_2022]. Lastly, region specifies the
geographical region of each respondent, identified using a unique code
for Nigerian states. This table not only demonstrates the diversity of
the dataset but also highlights the breadth of demographic and
governance-related variables included for analysis.

```{r}
#| label: tbl-summary-statistics
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| tbl-cap: "Detailed Summary Statistics of the Cleaned Dataset"

@@

# Ensure the age_group column is a character for correct mapping
cleaned_data <- cleaned_data %>%
  mutate(age_group = as.character(age_group))

# Function to calculate the mode (most frequent category)
calculate_mode <- function(x) {
  x <- na.omit(x)
  unique_x <- unique(x)
  unique_x[which.max(tabulate(match(x, unique_x)))]
}

# Adjust line breaks for proper rendering
line_break <- ifelse(knitr::is_html_output(), "<br>", "\n")

# Prepare the data for the transposed table
transposed_summary <- tibble(
  Statistic = c(
    "Most Frequent Age Group", 
    "Urban Percentage", 
    "Male Percentage", 
    "Corruption Counts", 
    "Education Counts"
  ),
  Value = c(
    calculate_mode(cleaned_data$age_group), 
    paste0(round(mean(cleaned_data$urban_rural == "Urban Residents", na.rm = TRUE) * 100, 2), "%"),
    paste0(round(mean(cleaned_data$gender == "Male", na.rm = TRUE) * 100, 2), "%"),
    paste0(
      "None: 61", line_break,
      "Some: 574", line_break,
      "High: 593", line_break,
      "All: 328"
    ),
    paste0(
      "Primary: 203", line_break,
      "Secondary: 173", line_break,
      "University: 102", line_break,
      "Postgraduate: 07"
    )
  )
)

# Generate a formatted table
kable(
  transposed_summary, 
  col.names = c("Statistic", "Value"),
  caption = "Detailed Summary Statistics of the Cleaned Dataset (Transposed)",
  escape = FALSE # Disables escaping for proper HTML/PDF formatting
) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  column_spec(2, width = "20em") # Adjust width for better multiline display

@@

```{r}
#| label: fig-education-vs-corruption
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Relationship between Education Levels and corruption percetpions in Nigeria  in Nigeria"

@@

# Create the stacked bar chart
ggplot(corruption_vs_urban, aes(x = urban_rural, y = proportion, fill = corruption_presidency)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(
    title = "Relationship between Rural vs. Urban Respondents and Corruption Perceptions",
    x = "Respondent Location",
    y = "Proportion of Respondents",
    fill = "Corruption Perception"
  ) +
  theme_minimal() +
  scale_fill_brewer(palette = "Set2") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5)
  )

@@

The relationship between respondents' residential location (rural vs.
urban) and their perceptions of corruption is shown in
@fig-ruralurban-versus-corruption Each bar represents the proportion of
respondents within rural and urban groups who hold different corruption
perceptions.

The chart shows that rural and urban respondents share similar
patterns of corruption perception. The majority of respondents in both
groups fall under the Some Corruption and High Corruption categories,
with Some Corruption being slightly more prevalent. The All Corrupt
category is the third most common perception in both groups, while the
No Corruption category is consistently the least represented.

@@

@fig-gender-versus-corruption shows the the relationship between
respondents' gender (male and female) and their perceptions of
corruption. Each panel represents one gender, displaying the count of
respondents across four corruption perception categories: All Corrupt,
High Corruption, Some Corruption, and No Corruption.

@@

The threshold parameters ($\alpha_j$) separate the ordered categories of
the outcome variable, while the Dirichlet prior for $\pi_{ij}$ assumes
no strong prior preference for any specific corruption category.

The use of these priors provides flexibility for the model while
preventing overfitting. The posterior distributions for the coefficients
and thresholds, along with diagnostic checks for model convergence and
predictive accuracy, can be found in the Appendix.

@@

# Extract summary
model_summary <- broom.mixed::tidy(bayesian_model)

# Render as a table
knitr::kable(
  model_summary,
  caption = "Summary of the Bayesian Model",
  digits = 2
) %>%
  kableExtra::kable_styling()

The analysis revealed distinct trends in Corruption perceptions in
different demographics. Our results are summarized in @tbl-modelresults. 
This presents the estimated coefficients and standard
errors for each predictor included in the model. The dependent variable
is the perception of corruption in the presidency, categorized into
ordered levels. The table includes predictors such as education level,
gender, urban or rural location, and agre group, which are modeled to
explain variations in corruption perceptions. Each predictor's
coefficient represents its effect on the log odds of perceiving
corruption in the presidency at a specific level relative to lower
levels, holding other variables constant.

Higher education levels(e.g., university or post-graduate
qualifications) arre associated with positive effects on corruption
perceptions, indicating a greater likelihood of perceived higher levels
of corruption. Begin female shows a small positive association with
higher corruption perceptions. Residing in rural areas is negatively
associated with corruption perceptions, suggesting lower perceptions of
corruption compared to urban counterparts. Agegroups show minimal
variation in their association with corruption perceptions, with no
significant deviations observed among different age brackets.

@@

# Simulating or using your posterior data
predicted_data <- data.frame(
  Predictor = names(coef(bayesian_model)),
  Estimate = coef(bayesian_model)
)

@@

This paper looks into the demographic disparities of corruption
perception in the Nigerian presidency, using survey data to examine
variables like education, gender, age and urban versus rural residence.
By looking at these factors, the study aims to inform targeted
anti-corruption camapigns and policy making. The Bayesian modeling
approach helps us understand the relationship between corruption
perceptions and these demographic variables.

@@

The relationship between education and corruption perceptions shows that
respondents with secondary school education are the most likely to
perceive high levels of corruption in the presidency. This supports
broader research showing that moderate levels of education are linked to
increased political awareness and accountability demands, as individuals
in this group are better equipped to identify systemic corruption but
may lack the structural access to address it effectively
[@transparency2019]. Individuals with higher education, such as
university graduates, report more moderate corruption perceptions, this
might largely beceause of their exposure to diverse viewpoints and
greater access to institutional frameworks that allow for political
skepticism. These suggest that anti-corruption campaigns targeting this
moderately educated demographic should focus on actionable reforms and
accountability mechanisms to harness their heightened awareness
productively [@u4nigeria2023].

@@

## Ethics considerations {#sec-ethics}

@@

These practices align with established ethical principles in social science research, including those outlined by the World Association for Public Opinion Research [@waporethics].

@@

@@

@fig-demo The figure provides an overview of demographic variables and corruption perceptions from the Afrobarometer Nigeria Round 9 survey. Rural residents constitute a larger share of the sample, aligning with Nigeria's predominantly rural demographic landscape. Corruption perception data shows that "High Corruption" and "Some Corruption" dominate public opinion. The education level distribution highlights the prevalence of basic education, with the majority of respondents having completed secondary school. Finally, the age distribution indicates that the 25–34 age group is the most represented cohort, suggesting that young adults play a crucial role in shaping perceptions of corruption and governance in Nigeria.
![Demographic Distributions of the Afrobarometer Data](combined_plot.png){#fig-demo width="120%"}

# Model details {#sec-model-details}

## Posterior Predictive Check

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheck
#| fig-cap: "Posterior Predictive Check for the Bayesian ordinal logistic regression model."

@@

## Diagnostics

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-diagnostic-traceplot
#| fig-cap: "Trace plot for selected parameters in the Bayesian ordinal logistic regression model."

>>>>

---
title: "Shaping Anti-Corruption Campaigns in Nigeria"
subtitle: "Youth Populations, Urban Areas and Moderately Educated Citizens Are Important for Anti-Corruption Campaigns "
author: 
  - Fatimah Yunusa
thanks: "Code and data are available at:https://github.com/fatimahsy/Nigeria_Democracy-"
date: today
date-format: long
abstract: "Peceptions of corruption in the Nigerian presidency vary significantly across demogrpahic groups. Using Afrobarometer survey data and Bayesisan ordinal logistic regression, this study looks at how education, gender, age, and urban versus rural residence influence these perceptions. The results show that urban residents and younger individuals are more likely to perceive high corruption, while rural populations and those with higher education show views that are moderate. These results show the need for targeted anti-corruption campaigns to adress demographic differences and imporve governance and accountability in Nigeria"
format: pdf
toc: true
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

Corruption is a big challenge to governance and development in Nigeria as a result of its ability to undermine public trust and economic growth. As the United Nations Office on Drugs and Crime (UNODC) stated, "corruption affects the lives of ordinary Nigerian, impeding development and eroding public trust in institutions [@corruptionsurvey2024]. This paper looks into the role of demographic factors-education,gender,age, and urban versus rural residence-in shaping perceptions of corruption in the Nigerian presidency.

Primarily, this paper is aimed at understanding how different demographic groups perceive corruption in the Nigerian presidency and to identify ways this can help improve anti-corruption campaigns, While existing studies have largely been focused on the institutional dynamics, there seems to be a lack of demographic-specific analysis within the Nigerian context. This paper addresses this by making these demographics the focus. It does this by using nationally representative data from Afrobarometer [@afrobarometer2023], a leading survey initiative capturing public attitudes on governance, democracy, and corruption across Africa. A Bayesian ordinal logistic regression was used to find patterns in how education, gender, age, and geographic location influence perceptions of corruption.

Our paper shows that there are a lot of disparities in corruption perceptions across demographic groups. Younger respondents and urban residents have higher perceptions of corruption, likely because of higher exposure to investigative media and political discourse. In contrast, rural populations-often reliant on patronage systems- tend to report more neutral views. Education also plays an important role since we find that secondary school graduates have the highest corruption perceptions.

Understanding these demographic differences is important for designing effective anti-corruption campaigns. Making sure outreach efforts are tailored to the unique experiences and perceptions of different demographic groups can increase their effectiveness and increase public trust. For example, youth-focused campaigns that use social media platforms and urban outreach using investigative journalism can engage the people. At the same time, localized, culturally appropriate campaigns in rural areas can address the different needs of these populations. As the UNODC emphasizes, "targeted and effective anti-corruption policies will improve lives of Nigerian citizens" [@afrobarometer2023].

The remainder of this paper is structured as follows; @sec-data details the data used for this paper, @sec-model introduces the Bayesian ordinal logistic regression model used to study the relationship between our variables of interest. @sec-results presents the findings from the model, detailing how different demographic factors like education and age affect corruption perception in Nigeria. @sec-discussion examines these results, discussing their implications for anti-corruption policies, weaknesses and next steps. @sec-survey-appendix explores the details of the Afrobarometer survey. @sec-model-details shows plots for Posterior predictive checks and Diagnostics as well as their analysis. @sec-survey-appendix details the survey methodology used in the Afrobarometer data and @sec-ethics addresses very important ethical principles and the ethical challenges of surveying sensitive topics like corruption.@sec-Data-Driven-Narrative-appendix introduces a narrative example, 'Amina's Story,' to humanize the data by showing how demographic factors like age, education, and urban residency shape individual perceptions of corruption, while emphasizing the ethical importance of considering the lived experiences behind the data.

@@

For this analysis, i use the Afrobarometer Round 9, Nigeria survey. 
Afrobarometer conducts surveys that are nationally
representative across African nations to capture public perceptions on
topics like governance, democracy, and economic issues. The Nigerian
Round 9 survey dataset contains responses from 1,556 people and shows
the diverse demographic statistics across gender, region, and residence
type(urban or rural). The data is freely available on the Afrobarometer
website[@afrobarometer2023] and was collected through a multi-stage,
stratified sampling method. This is to ensure representativeness and
enables analysis of different demographics and socioeconomic indicators.

@@

The data for this study was downloaded, cleaned, analyzed, modeled, and
visualized using R [@citeR], a statistical programming language.[@afrobarometer2023] served as the primary data source, providing importantsurvey data for analysis.***Telling Stories with Data*** [@tellingstories] was referenced for its methodologies. The
following packages were used:

-   **`modelsummary`** [@modelsummary]: Used to create well-formatted
    regression tables and summaries.
-   **`rstanarm`** [@rstanarm]: Facilitated Bayesian regression modeling
    using the Stan backend.
-   **`dplyr`** [@dplyr]: Streamlined data manipulation, transformation,
    and summarization processes.
-   **`here`** [@here]: Simplified the organization of file paths,
    improving project reproducibility.
-   **`arrow`** [@arrow]: Enabled efficient handling of large datasets
    with fast reading and writing capabilities.
-   **`bayesplot`** [@bayesplot]: Assisted in producing diagnostic
    checks and posterior predictive visualizations for Bayesian models.
-   **`ggplot2`** [@ggplot2]: Provided extensive tools for creating
    clear and impactful visualizations.
-   **`patchwork`** [@patchwork]: Combined multiple plots into cohesive,
    professional visuals.
-   **`knitr`** [@knitr]: Enabled dynamic report generation, integrating
    code, output, and text seamlessly.
-   **`kableExtra`** [@kableExtra]: Enhanced table styling and
    formatting for clean, professional presentations.
-   **`ggalt`** [@ggalt]: Allowed the creation of specialized plots,
    enhancing the depth of data visualizations.
-   **`haven`** [@haven]: Facilitated the import of `.sav` survey data
    from the Afrobarometer.
-   **`broom.mixed`** [@broommixed]: Streamlined the extraction and
    tidying of results from mixed models for easy analysis and
    visualization.

@@

# Generate a table using kableExtra
kable(
  table_preview, 
  caption = "Preview of the Cleaned Dataset"
) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

@tbl-cleaned-data-preview represents the first six cleaned rows of the
dataset, showing the important variables used in the analysis. The
variables were constructed from specific survey questions in the
Afrobarometer Round 9 Nigeria Survey [@afrobarometer2023], which
captures several socioeconomic sentiments within the country.The column
`corruption_presidency` captures perceptions of corruption within the
office of the presidency, derived from responses to the question, *“How
many of the following people do you think are involved in corruption, or
haven’t you heard enough about them to say: the president and officials
in his office?”* The variable education reflects respondents' highest
level of education completed, gathered from the question, *“What is the
highest level of education you have completed?”* The gender variable
indicates the respondent's gender, collected through direct demographic
inquiry. The column age_group categorizes respondents into age brackets
based on the question,* “How old are you?”* The urban_rural variable
distinguishes between urban and rural respondents, as recorded by
interviewers based on the primary sampling unit (PSU) during data
collection [@survey_manual_2022]. Lastly, region specifies the
geographical region of each respondent, identified using a unique code
for Nigerian states. This table not only demonstrates the diversity of
the dataset but also highlights the breadth of demographic and
governance-related variables included for analysis.

```{r}
#| label: tbl-summary-statistics
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| tbl-cap: "Detailed Summary Statistics of the Cleaned Afrobarometer Dataset"

@@

# make sure the age_group column is a character for correct mapping
cleaned_data <- cleaned_data %>%
  mutate(age_group = as.character(age_group))

# Function to calculate the mode 
calculate_mode <- function(x) {
  x <- na.omit(x)
  unique_x <- unique(x)
  unique_x[which.max(tabulate(match(x, unique_x)))]
}

line_break <- ifelse(knitr::is_html_output(), "<br>", "\n")

# data for the transposed table
transposed_summary <- tibble(
  Statistic = c(
    "Most Frequent Age Group", 
    "Urban Percentage", 
    "Male Percentage", 
    "Corruption Counts", 
    "Education Counts"
  ),
  Value = c(
    calculate_mode(cleaned_data$age_group), 
    paste0(round(mean(cleaned_data$urban_rural == "Urban Residents", na.rm = TRUE) * 100, 2), "%"),
    paste0(round(mean(cleaned_data$gender == "Male", na.rm = TRUE) * 100, 2), "%"),
    paste0(
      "None: 61", line_break,
      "Some: 574", line_break,
      "High: 593", line_break,
      "All: 328"
    ),
    paste0(
      "Primary: 203", line_break,
      "Secondary: 173", line_break,
      "University: 102", line_break,
      "Postgraduate: 07"
    )
  )
)

# formatted table
kable(
  transposed_summary, 
  col.names = c("Statistic", "Value"),
  caption = "Detailed Summary Statistics of the Cleaned Dataset (Transposed)",
  escape = FALSE 
) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  column_spec(2, width = "20em")

@@

```{r}
#| label: fig-education-vs-corruption
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Relationship between Education Levels and corruption percetpions in Nigeria"

@@

# Create the stacked bar chart
ggplot(corruption_vs_urban, aes(x = urban_rural, y = proportion, fill = corruption_presidency)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(
    title = " Rural vs. Urban Respondents & Corruption Perceptions",
    x = "Respondent Location",
    y = "Proportion of Respondents",
    fill = "Corruption Perception"
  ) +
  theme_minimal() +
  scale_fill_brewer(palette = "Set2") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5)
  )

@@

The relationship between respondents' residential location (rural vs.
urban) and their perceptions of corruption is shown in
@fig-ruralurban-versus-corruption Each bar represents the proportion of
respondents within rural and urban groups who hold different corruption
perceptions.The chart shows that rural and urban respondents share similar
patterns of corruption perception. The majority of respondents in both
groups fall under the "Some Corruption" and "High Corruption" categories,
with "Some Corruption" being slightly more prevalent. The "All Corrupt"
category is the third most common perception in both groups, while the
"No Corruption" category is consistently the least represented.

@@

@fig-gender-versus-corruption shows the relationship between
respondents' gender (male and female) and their perceptions of
corruption. Each panel represents one gender, displaying the count of
respondents across four corruption perception categories: All Corrupt,
High Corruption, Some Corruption, and No Corruption.

@@

The threshold parameters ($\alpha_j$) separate the ordered categories of
the outcome variable, while the Dirichlet prior for $\pi_{ij}$ assumes
no strong prior preference for any specific corruption category.The use of these
priors provides flexibility for the model while preventing overfitting. The 
posterior distributions for the coefficients and thresholds, along with 
diagnostic checks for model convergence and predictive accuracy, can be found in
the Appendix.

@@

detailed_model_summary <- broom.mixed::tidy(bayesian_model, conf.int = TRUE, effects = "fixed") %>%
  select(term, estimate, std.error, conf.low, conf.high)

# Render as a clean table
knitr::kable(
  detailed_model_summary,
  caption = "Detailed Summary of the Bayesian Model with Credible Intervals",
  digits = 3,
  col.names = c("Term", "Estimate", "Std. Error", "2.5% CI", "97.5% CI")
) %>%
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::add_header_above(c(" " = 1, "Fixed Effects" = 4))
```

The analysis revealed trends in corruption perceptions in
different demographics. Our results are summarized in @tbl-modelresults. 
This presents the estimated coefficients and standard
errors for each predictor included in the model. The dependent variable
is the perception of corruption in the presidency, categorized into
ordered levels. The table includes predictors such as education level,
gender, urban or rural location, and agre group, which are modeled to
explain variations in corruption perceptions. Each predictor's
coefficient represents its effect on the log odds of perceiving
corruption in the presidency at a specific level relative to lower
levels, holding other variables constant.

Higher education levels(e.g., university or post-graduate
qualifications) are associated with positive effects on corruption
perceptions, indicating a greater likelihood of perceived higher levels
of corruption. Being female shows a small positive association with
higher corruption perceptions. Residing in rural areas is negatively
associated with corruption perceptions, suggesting lower perceptions of
corruption compared to urban counterparts. Age groups show minimal
variation in their association with corruption perceptions, with no
significant deviations observed among different age brackets.

@@

# Loading in posterior data
predicted_data <- data.frame(
  Predictor = names(coef(bayesian_model)),
  Estimate = coef(bayesian_model)
)

@@

This paper looks into the demographic disparities of corruption
perception in the Nigerian presidency, using survey data to examine
variables like education, gender, age and urban versus rural residence.
By looking at these factors, the study aims to inform targeted
anti-corruption campaigns and policy making. The Bayesian modeling
approach helps us understand the relationship between corruption
perceptions and these demographic variables.

@@

The relationship between education and corruption perceptions shows that
respondents with secondary school education are the most likely to
perceive high levels of corruption in the presidency. This supports
broader research showing that moderate levels of education are linked to
increased political awareness and accountability demands, as individuals
in this group are better equipped to identify systemic corruption but
may lack the structural access to address it effectively
[@transparency2019]. Individuals with higher education, such as
university graduates, report more moderate corruption perceptions, this
might largely be because of their exposure to diverse viewpoints and
greater access to institutional frameworks that allow for political
skepticism. These suggest that anti-corruption campaigns targeting this
moderately educated demographic should focus on actionable reforms and
accountability mechanisms to harness their heightened awareness
productively [@u4nigeria2023].

@@

## Ethical considerations {#sec-ethics}

@@

These practices are aligned with ethical principles in social science research, including those outlined by the World Association for Public Opinion Research [@waporethics].

@@

# Amina's Story - A Personal Perspective {#sec-Data-Driven-Narrative-appendix}

Amina is a 25-year-old woman living in Lagos, Nigeria. She works long hours at Balogun Market, navigating the daily challenges of urban life. She recently completed university, an achievement she’s proud of, and dreams of one day pursuing higher education. But like many young Nigerians, Amina often feels frustrated and disillusioned when it comes to governance and corruption.

In conversations with her friends and colleagues, Amina’s voice often reflects anger and disappointment. She believes corruption in the presidency is widespread, a sentiment shared by many in her age group and educational background, as revealed in the survey data. Growing up in Lagos, where access to news and social media is plentiful, Amina has been exposed to stories of corruption and unfulfilled promises. This exposure has shaped her outlook, making her skeptical of government accountability.

Amina’s experiences highlight the role of demographic factors in shaping perceptions of corruption. Her youth connects her to a generation that is more vocal about demanding accountability, while her urban residency exposes her to more information about governance. At the same time, her level of education gives her the tools to critically analyze these issues, though it also fuels her frustration when systemic problems persist.

Reflecting on Amina’s story reminds us of the ethical responsibility to consider the individuals behind the data. Every statistic represents a life, a struggle, and a hope for change. By thinking of people like Amina, policymakers and campaigners can design anti-corruption initiatives that genuinely resonate with those they aim to serve. Ethical actions begin with understanding these lived realities, ensuring that interventions are meaningful and respectful of the diverse experiences within the population.

@@

This figure provides an overview of demographic variables and corruption perceptions from the Afrobarometer Nigeria Round 9 survey. Rural residents constitute a larger share of the sample, aligning with Nigeria's predominantly rural demographic landscape. Corruption perception data shows that "High Corruption" and "Some Corruption" dominate public opinion. The education level distribution highlights the prevalence of basic education, with the majority of respondents having completed secondary school. Finally, the age distribution indicates that the 25–34 age group is the most represented cohort.

![Demographic Distributions of the Afrobarometer Data](combined_plot.png){#fig-demo width="110%"}

# Model details {#sec-model-details}
## Posterior Predictive Check
```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheck
#| fig-cap: "Posterior Predictive Check for the Bayesian ordinal logistic regression model."

@@

## Diagnostics
```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-diagnostic-traceplot
#| fig-cap: "Trace plot for selected parameters in the Bayesian ordinal logistic regression model."
